Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-02 paper/ms.tex
Clean up data section

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone\
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\
    along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
  \caption{Difference in abundances of this pair and other wide binaries in
    \citealt{2016ApJS..225...32B}.
    Additionally, we show the distribution of abundance difference
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
    similar to \bizarreone\ and \sunanalog.
    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
    Thus, the narrower range of in $\Delta\feh$ is by construction.
    First, we see that most of the other comoving wide binaries included in \citealt{2016ApJS..225...32B}
    have small ($<0.1$~dex) differences in all elements making a difference of $\approx 0.2$~dex seen in
    \bizarreone-\sunanalog\ pair rare.
    Second, random pairings of disk stars with similar $\Delta\feh$ usually show
    similar enhancement in all other elements.
    %Notably, the relative depletion of \elem{Na} and \elem{Mn} with respect to \elem{Fe}
    %suggests that even when we assume \bizarreone\ and \sunanalog\ are of different origin,
    %Galactic evolution cannot explain the difference.
  }
  \label{fig:deltaXH}
\end{figure}

@@

%In all components, the pair is consistent with being comoving and close in
%separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
%but the median 3-space separation is $\approx$$0.6~\pc$.

%\begin{figure}[htbp]
%  \begin{center}
%    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
%  \end{center}
%  \caption{%
%    Differences in posterior samples over Galactocentric phase-space coordinates
%    for the two stars \sunanalog\ and \bizarreone.
%    \label{fig:dxdv}}
%\end{figure}

%\figname~\ref{fig:orbit} shows an orbit computed from the median posterior
%sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
%in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
%explain}
%The Sun's orbit in this same Milky Way model is under-plotted for comparison
%(grey line); the orbits of the stars in this pair have large scale-heights
%relative to the Sun's orbit despite being young.

%\begin{figure}[htbp]
%  \begin{center}
%    \includegraphics[width=\linewidth]{orbits.pdf}
%  \end{center}
%  \caption{%
%    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
%    For \sunanalog\, the initial conditions are set to the median posterior
%    sample over the inferred 6D phase-space coordinates.
%    The orbits are computed by integrating backwards from the present-day
%    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
%    Leapfrog integration scheme implemented in \project{Gala}
%    (\citealt{Gala:2017}). \todo{APW: citation...}
%\label{fig:orbit}}
%\end{figure}

@@

We stress that none of the other four twin-like ($\Delta T_mathrm{eff} \lesssim 100$~K)
wide binary pairs examined in \citealt{2016ApJS..225...32B} show discrepancies in abundances between the
stars at this level (\figname~\ref{fig:deltaXH}).
As shown in \figname~\ref{fig:deltaXH}, 
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.
(see figure X in that paper; purple is this pair)
Moreoever, the abundance differences cannot be due to different chemical enrichment
history in the disk even if the two stars were of different origin.
\figname~\ref{fig:deltaXH} shows the distribution of $\Delta[\elem{X}/\elem{H}]$
for random pairings of two stars from similar \feh\ as \bizarreone\ and \sunanalog
as violins for each element.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are enhanced at a similar level with some variations.
% Clean up:
% Specifically, it is very unlikely that the star 
% The abundance of \bizarreone\ is peculiar on its own compared to other disk
stars with similar \feh.
%For a star with $\feh \approx 0.2$ like \bizarreone, we generally expect
%$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
%(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of \bizarreone\
%very unlikely to arise from Galactic chemical evolution.

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distribution is consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: ref for vertical action as age?
Finally, their fiducial orbit in a Milky Way-like potential show that the vertical action
for this pair is larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main sequence
stars, and that their unusually high \elem{Li} abundance requires an alternative explanation.

@@

We discuss the possible origins of this pair.
Let us first consider scenarios in which the two stars are not actually born together.

@@

In regions where binarity fraction is high, binary-binary scattering may be more important
than binary-single scattering (\todo{CITE})

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaXH_elem_violins.pdf}
  \caption{Abundance difference in this pair and other twin-like
    ($\Delta T_\mathrm{eff}\lesssim 100$~K) wide binaries in
    \citealt{2016ApJS..225...32B}.
    The differences in other pairs are small ($<0.05$~dex)
    for all elements except \elem{N} and \elem{O} which are the most
    uncertain, making the difference of $\approx 0.2$~dex seen in
    \bizarreone-\sunanalog\ rare.
    Additionally, we show the distribution of abundance differences
    between stars with similar metallicity difference
    ($\Delta[\elem{Fe}/\elem{H}] \approx 0.2$)
    as violins with medians indicated by black line segments
    by randomly pairing up single stars in \citealt{2016ApJS..225...32B} at two metallicity bins,
    $-0.025 < \feh < 0.025$ (160 stars) and $1.975 > \feh > 2.025$ (137 stars),
    similar to \bizarreone\ and \sunanalog.
    The difference is always taken to be $\mathrm{higher}\,\feh - \mathrm{lower}\,\feh$.
    Thus, the narrower range of in $\Delta\feh$ is by construction.
    Random pairings of disk stars with similar $\Delta\feh$ usually show
    similar enhancement in all other elements
    unlike the pattern seen in \bizarreone-\sunanalog\ pair.
  }
  \label{fig:deltaXH}
\end{figure}

@@

@@

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk})
are less than $0.05$~dex, makiing \bizarreone-\sunanalog\ pair an outlier.
Moreoever, the abundance differences cannot be due to different chemical enrichment
history in the disk even if the two stars were of different origin.
\figname~\ref{fig:deltaXH} additioanlly shows the distribution of $\Delta[\elem{X}/\elem{H}]$
for random pairings of two stars with similar \feh\ as \bizarreone\ and \sunanalog
as violins for each element.
We see that when a star is enhanced in $\elem{Fe}$ by $0.2$~dex,
all other elements are enhanced at a similar level with some variations.
Specifically, for a typical star with $\elem{Fe} \approx 0.2$~dex,
we generally expect $[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa})
making the low $\elem{Na}/\elem{Fe}$ and $\elem{Mn}/\elem{Fe}$ seen in \bizarreone\
very unlikely to arise from variations in Galactic chemical evolution.

% HOGG to provide some theoretical account adding to the above empirical evidence.

@@

In fact, the surface lithium abundance is the only indication that points to younger ages.
If the two stars are indeed only several hundred Myrs old at most,
they are expected to be part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving pairs
using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars are often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have looked for these signs for the pair to find none, and their spectral energy
distributions are consistent with blackbody.
The low $v\sin(i)$ values also argue against very young ages inferred from the
surface lithium abundances.
% TODO: reference for vertical action as age?
Finally, the pair's fiducial orbit in a axisymmeric Milky Way-like potential
has a vertical action larger than the Sun, favoring an older age.
We concluded that the two stars are most likely coeval, $\sim 4$~Gyr old main
sequence stars, and that their unusually high \elem{Li} abundance requires an
alternative explanation.

@@

We discuss the possible origins of the peculiar abundance differences of
\bizarreone-\sunanalog.
Although the data described above strongly suggests that the two stars are
coeval, let us first consider scenarios in which the two stars are not actually
born together.

@@

%LEIGH
